\cvsection{Projects}

\begin{cventries}

  \cventry
  {Senior Capstone Project: Quantum Optimization Algorithms}
  {\textbf{Undergraduate Research Project}}
    {Lubbock, TX, USA}
    {Apr. 2020 -- May 2021}
    {
      \begin{cvitems}
        \item{Conducting research work done under the supervision of Dr. Ismael Regis de-Farias in collaboration with National Laboratory of Scientific Computing (LNCC) of Brazil}
        \item{Implemented methods to calculate Hilbert-Schmidt-Product and decompose any given square matrix into sum of Pauli matrices}
        \item{Created a computational framework for testing Variational Quantum Eigensolver (VQE) Algorithms}
        \item{Initiated a study to explore the dynamics of changing each component - \textit{Hermitian matrix type, variational form, circuit depth} and \textit{optimizer} - used in the VQE routine by conducting sensitivity analyses on two performance metrics – time taken to solve the problem and accuracy of the solution}
        \item{Contributed to the development efforts of NEBLINA - a Quantum Random Walk Simulator Software Suite}
      \end{cvitems}
    }

  \cventry
  {Setting Up K\textit{i}m Lab and FDTD Analysis of Silicon Carbide (SiC) Permittivity}
  {\textbf{Undergraduate Research Project}}
    {Lubbock, TX, USA}
    {Nov. 2019 -- Apr. 2020}
    {
      \begin{cvitems}
      \item{Collaborated with University of Texas, Rio Grande Valley to conduct experiments and record the permeability value of SiC}
      \item{Verified the recorded data by simulating a 2D FDTD implementation of the experimental condition}
      \item{Volunteered in setting up K\textit{i}m lab for Infrared optics \& polarimetry for novel quantum system and nanostructures}
      \item{Supervisor: Myoung-Hwan Kim, PhD.}
      \end{cvitems}
    }

  \cventry
  {Geometric Optics: Modelling Scalar Irradiance of light sources under water}
  {\textbf{Undergraduate Research Project}}
    {Lubbock, TX, USA}
    {Aug. 2018 -- May. 2019}
    {
      \begin{cvitems}
      \item{Assisted Masud (Math PhD candidate) with his thesis by accepting to take on one of his problems as my project}
  \item{Created a mathematical model for the downwards scalar irradiance of light from ﬁrst principles}
  \item{Discovered that the derived model is exponentially more accurate than the traditional model of Lambert-Beer at optical densities greater than 0.4 in the context of water bodies.}
      \end{cvitems}
    }

  \cventry
  {Web Application for a Health Care System}
  {\textbf{Undergraduate Academic Project: \textit{Software Engineering 1}}}
    {Lubbock, TX, USA}
    {Sept. 2020 -- Present}
    {
      \begin{cvitems}
      \item{Developed the static model for the healthcare system}
    \item{Documented the interaction model that depicts objects participating in each use case and the sequence of interactions among the objects}
    \item{Designed database tables to store information about appointments, patient charts, payments, and reports in the healthcare system.}
    \item{Implemented the program in JAVA using XXX libraries}
      \end{cvitems}
    }

  \cventry
  {Design and Implementation of AI used in Bang! The Dice Game}
  {\textbf{Undergraduate Academic Project: \textit{Object Oriented Programming}}}
    {Lubbock, TX, USA}
    {Apr. 2020 - May 2020}
    {
      \begin{cvitems}
      \item{Utilized ideas of Probabilistic State Vectors and Unitary Evolutions from Quantum Mechanics to model AI behavior for Bang! the Dice Game}
      \item{Implemented concepts Markov Decision Processes (MDP) to simulate AI gameplay with a Human user}
      \item{Documented, debugged and conducted various test cases to ensure AI reliability and robustness}
      \end{cvitems}
    }

  \cventry
  {Dynamics of a laser propelled nanocraft on a fly by mission to Proxima Centauri B}
  {\textbf{Physics Competition Project (Undergraduate)}}
    {Lubbock, TX, USA}
    {Nov. 2018}
    {
      \begin{cvitems}
      \item{Modelled the design and trajectory needed for a light sail propelled nanocraft to the nearest star system Alpha Centauri in order to perform a flyby of Proxima Centauri b subject to various constraints defined by the University Physics Competition Committee}
      \item{Co-authored a research paper addressing the problem uder 48 hours as per the guidelines of the competition}
     \item{Won the Silver Medal for our efforts}
      \end{cvitems}
    }

% ========================== PERSONAL PROJECTS BELOW ====================
  %\cventry
  %{Calculus Analysis Software}
  %{\textbf{Personal Project}}
    %{}
    %{Sept. 2020 -- Present}
    %{
      %\begin{cvitems}
      %\item{plots functions}
      %\item{symbolic differentiation}
      %\item{numerical integral (simpsons and euler)}
      %\item{latex printout}
      %\end{cvitems}
    %}

  %\cventry
  %{Natural Tree Design generation through Randomness and Fractal Geometry}
  %{\textbf{Personal Project}}
    %{}
    %{Jul. 2020 -- Present}
    %{
      %\begin{cvitems}
      %\item{recursion and randomness}
      %\item{idea needs implementation - explain in brief}
      %\end{cvitems}
    %}

  %\cventry
  %{Analysis of Stock Market Trends Using Integral Transforms}
  %{\textbf{Personal Project}}
    %{}
    %{Jul. 2020 -- Present}
    %{
      %\begin{cvitems}
      %\item{idea}
        %\item{present status}
      %\end{cvitems}
    %}

\end{cventries}
