\cvsection{Talks \& Presentations}

\begin{cvhonors}

    \cvhonor
    {Invited Lectures for Quantum Design Workshop @ \textsc{UCLA}} 
    {\textit{\scriptsize "Learning Inverse Design Maps using ML for Physics Discovery" and "Designing Fabrication-Ready Superconducting Quantum Chips"}}
    {Los Angeles, USA}
    {Mar. 2024}

    \cvhonor
    {SQuADDS: A validated design database and simulation workflow for superconducting qubit design}
    {\textit{\scriptsize APS Global Physics Summit}}
    {Anaheim, USA}
    {Mar. 2024}

    \cvhonor
    {Invited Lectures}
    {\textit{\scriptsize Qiskit Fall Fest 2024 on Superconducting Quantum Hardware Research}}
    {Online}
    {Oct. 2024}

    \cvhonor
    {Poster and Talk at \textsc{Lincoln Labs}}
    {\textit{\scriptsize SQUILL User Foundry Meeting}}
    {Lexington, USA}
    {Jul. 2024}

    \cvhonor
    {Invited Lectures at \textsc{Fermilab}}
    {\textit{\scriptsize Qubit Design and ML Summer School}}
    {Online}
    {Jun. 2024}

    \cvhonor
    {Going from Hamiltonian to GDS File: An Open Source Package for Generating Qubit Designs}
    {\textit{\scriptsize APS March Meeting, 2024}}
    {Minneapolis, USA}
    {Apr. 2024}

    \cvhonor
    {Invited Talk at \textsc{Lincoln Labs}}
    {\textit{\scriptsize Introducing SQuADDS}}
    {Online}
    {Jan. 2024}

    \cvhonor
    {Invited Lectures on "How to be an Effective TA 101"}
    {\textit{\scriptsize PHYS 593: Practicum in Teaching Physics and Astronomy, \textsc{USC}}}
    {Los Angeles, USA}
    {2022-2024}

    \cvhonor
    {Quasiparticle Dynamics in Andreev Bound States Part 2: Photon Interactions}
    {\textit{\scriptsize APS March Meeting, 2023}}
    {Las Vegas, USA}
    {2023}

    \cvhonor
    {American Physical Society April Meeting}
    {\textit{\scriptsize Machine Learning in Muon Tomography Talk}}
    {Online}
    {2021}

    \cvhonor
    {Physics Departmental Colloquium}
    {\textit{\scriptsize Dancing in the "Muon" light}}
    {Lubbock, USA}
    {}

    \cvhonor
    {University Research Conference, \textsc{TTU}}
    {\textit{\scriptsize Economic Impact of Quantum Computers}}
    {Virtual}
    {}

    \cvhonor
    {SPS and Women In Physics (WiP) Programming Principles}
    {\textit{\scriptsize Speaker}}
    {Lubbock, USA}
    {}

    \cvhonor
    {SPS and Women In Physics (WiP) Introduction to Programming}
    {\textit{\scriptsize Speaker}}
    {Lubbock, USA}
    {2020}

    \cvhonor
    {Departmental Poster Competition, Department of Physics and Astronomy, \textsc{TTU}}
    {}
    {Lubbock, USA}
    {}

    \cvhonor
    {Quantum 2020 (Institute Of Physics) Virtual Conference}
    {\textit{\scriptsize Analysis of VQE Regimes in NISQ Era}}
    {Virtual}
    {}

    \cvhonor
    {Summer Showcase! at the Institute for Software Integrated Systems}
    {}
    {Tennessee, USA}
    {}

    \cvhonor
    {International Symposium on Transportation Data and Modeling (ISTDM)}
    {\textit{\scriptsize Postponed}}
    {Michigan, USA}
    {}

    \cvhonor
    {\textsc{TTU} Undergraduate Research Conference}
    {\textit{\scriptsize Muon Tomography Talk}}
    {Virtual Conference}
    {}

    \cvhonor
    {\textsc{TTU} Undergraduate Research Conference}
    {\textit{\scriptsize Autonomous Vehicle Model Poster}}
    {Virtual Conference}
    {}

    \cvhonor
    {Far West Section of American Physical Society (FWSAPS), \textsc{Stanford University}}
    {}
    {Stanford, USA}
    {2019}

    \cvhonor
    {Texas Section of American Physical Society (TSAPS)}
    {}
    {Lubbock, USA}
    {}

    \cvhonor
    {Departmental Poster Competition, Department of Physics and Astronomy, \textsc{TTU}}
    {}
    {Lubbock, USA}
    {}

    \cvhonor
    {International Conference for Physics Students 2019, \textsc{University of Köln}}
    {}
    {Köln, Germany}
    {}

    \cvhonor
    {Undergraduate Colloquium: Programming Principles}
    {\textit{\scriptsize SPS \textsc{TTU}}}
    {Lubbock, USA}
    {2018}

\end{cvhonors}
