\cvsection{Training}

\cvsubsection{Summer schools}

\begin{cvhonors}

    \cvhonor
    {Summer School on Machine Learning and Big Data with Quantum Computing (SMBQ)}
    {University of Porto \& Polytechnic Institute of Porto}
    {Virtual}
    {Sept. 2020}

    \cvhonor
    {Lunch and Learn Lecture Series}
    {Cyber-Phyical Systems Virtual Organisation (CPS VO) }
    {Tennessee, USA}
    {Jun. - Aug. 2020}

    \cvhonor
    {Qiskit Global Summer School}
    {IBM}
    {International}
    {Jul. 2020}

\end{cvhonors}

\cvsubsection{Workshops}

\begin{cvhonors}

    \cvhonor
    {ALD Leads Certified: Leadership Program}
    {Alpha Lambda Delta Honor Society}
    {Virtual}
    {In Process}

    \cvhonor
    {Quantum Week of Fun}
    {Cambridge Quantum Computing}
    {Virtual}
    {Nov. 2020}

    \cvhonor
    {Introduction to Parallel Computing}
    {TTU High Performance Computing Center (HPCC)}
    {Texas, USA}
    {Sept. 2020}


    \cvhonor
    {Basic Programming for Quantum Machine Learning}
    {National Institute for Theoretical Physics}
    {Virtual}
    {Sept. 2020}

    \cvhonor
    {A Progress Report from the Wolfram Physics Frontier}
    {Neural Engineering Research Venture (NERV)}
    {}
    {Virtual}
    {Jul. 2020}

    \cvhonor
    {Cybersecurity Basics Training}
    {TTU}
    {Texas, USA}
    {Jun. 2020}

    \cvhonor
    {Career in Physics Workshop}
    {Stanford University}
    {California, USA}
    {Nov. 2019}

    \cvhonor
    {Customer Discovery and the Business Model Canvas for STEM innovations}
    {TTU Innovation Hub}
    {Texas, USA}
    {Oct. 2020}

    \cvhonor
    {Red Raider Startup Program}
    {TTU Innovation Hub}
    {Texas, USA}
    {Oct. 2018}

\end{cvhonors}


%\cvsubsection{Hackathons}

%\begin{cvhonors}
    %\cvhonor
    %{Hacklahoma 2020}
    %{Major League Hacking (MLH)}
    %{Oklahoma, USA}
    %{Mar. 2020}

%\end{cvhonors}
